\subsection{Work Package 4}

\begin{table}[hbpt]\centering
	\begin{tabular}{|p{0.35\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|
         p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|}\hline
		 Work package number& WP4 &
		 \multicolumn{4}{|c|}{Start date or starting event:}{}&
		 \multicolumn{2}{|c|}{                        4 }{}\\\hline
		 Work package title&\multicolumn{7}{|c|}{Semantic Analyzer}{}\\\hline
		 Activity Type&\multicolumn{7}{|c|}{ RTD }{}\\\hline
		 Participant number & 3 & 2 & 5 & 6 & ~ & ~ & ~ \\\hline
		 Person-months per participant: & 24 & 12 & 6 & 6 & ~ & ~ & ~ \\\hline
	\end{tabular}
\end{table}

\subsubsection{Objectives}
	\begin{itemize}
		\item O4.1 Create the Semantic Analyzer: The Semantic Analyzer should be able to translate source code into its formal equivalence. Translated text should be constructed in the way that it can be compared to formal requirements.
		
		The Semantic Analyzer have well defined interfaced so it can be built into popular and requested integrated development environment.
		\item O4.2 Present Research Work: The work should be summarized and be published as an article until M2.
	\end{itemize}

\subsubsection{Description of work}
	\begin{itemize}
		\item O4.1 Create the Semantic Analyzer
		\begin{itemize}
			\item T4.1.1: The \gls{KTH} team should define the architecture for the Semantic Analyzer. The architecture should be adequate for the task at hand.
			\item T4.1.2: The architecture has to be documented and presented to the stakeholders until M2.
			\item T4.1.3: The translated formal description should be analyzed and tested. Detailed report of both source code and its translated equivalence should be created. 
			\item T4.1.4: The Semantic Analyzer should be validated by independent comity as a prove of its correctness.
		\end{itemize}
	
		\item O4.2 Present Research Work
		\begin{itemize}
			\item T4.2.1: The work should be summarized and be published as an article until M2. 
		\end{itemize}
	\end{itemize}
\subsubsection{Deliverables}
	\begin{itemize}
		\item D4.1 First Semantic Analyzer Prototype : The first prototype should be delivered at the end of the 8th months. It has to be able to run without crash and fulfill basic functionalities.
		\item D4.2 Final Semantic Analyzer Prototype : The final prototype should be delivered until M2 and it has to fulfill all functionalities.
		\item D4.3 Semantic Analyzer Project Paper : The project paper should be delivered until M2 and should contain the results of WP4.
	\end{itemize}