\subsection{Work Package 6}

\begin{table}[hbpt]\centering
	\begin{tabular}{|p{0.35\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|
         p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|}\hline
		 Work package number& WP6 &
		 \multicolumn{4}{|c|}{Start date or starting event:}{}&
		 \multicolumn{2}{|c|}{                        18 }{}\\\hline
		 Work package title&\multicolumn{7}{|c|}{ Verifier }{}\\\hline
		 Activity Type&\multicolumn{7}{|c|}{ RTD }{}\\\hline
		 Participant number & 2 & 1 & 3 & 4 & 7 & 8 & 9 \\\hline
		 Person-months per participant: & 30 & 25 & 25 & 25 & 5 & 5 & 5 \\\hline
	\end{tabular}
\end{table}

\subsubsection{Objectives}
	\begin{itemize}
		\item O6.1 Create the Verifier: The Semantic Analyzer should be able to compere outputs from \gls{NLP} and from Semantic Analyzer. Verifier's constructor shall be able to build the system and construct inputs in the way when same statements of requirement and code are compared.
		
		The Verifier should create a clear report of analyzed data, both in successful and unsuccessful results.
		\item O6.2 Present Research Work: The work should be summarized and be published as an article until M5.
	\end{itemize}

\subsubsection{Description of work}
	\begin{itemize}
	\item O6.1 Create the Semantic Analyzer
	\begin{itemize}
		\item T6.1.1: The \gls{Aalto} team should define the architecture for the Verifier. The architecture should be adequate for the task at hand.
		\item T6.1.2: The architecture has to be documented and presented to the stakeholders until M5.
		\item T6.1.3: The verified report should be analyzed and tested. Detailed report of compared objects and its result should be created. 
		\item T6.1.4: The Verifier should be validated by independent comity as a prove of its correctness
		\item T6.1.5 Conditional output should be created.
		\item T6.1.6 Interface to Code Fix Suggester should be defined in case if compared object are different and failed analysis
	\end{itemize}
	
	\item O6.2 Present Research Work
	\begin{itemize}
		\item T6.2.1: The work should be summarized and be published as an article until M5. 
	\end{itemize}
\end{itemize}

\subsubsection{Deliverables}
	\begin{itemize}
		\item D6.1 First Verifier Prototype : The first prototype should be delivered at the end of the 24th months. It has to be able to run without crash and fulfill basic functionalities.
		\item D6.2 Final Verifier Prototype : The final prototype should be delivered until M5 and it has to fulfill all functionalities.
		\item D6.3 Verifier Project Paper : The project paper should be delivered until M2 and should contain the results of WP6.
	\end{itemize}