\subsection{Work Package 1}

\begin{table}[hbpt]\centering
	\begin{tabular}{|p{0.35\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|
                     p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|}\hline
		 Work package number& WP1 &
		 \multicolumn{4}{|c|}{Start date or starting event:}{}&
		 \multicolumn{2}{|c|}{                        1  }{}\\\hline
		 Work package title&\multicolumn{7}{|c|}{ Project Management }{}\\\hline
		 Activity Type&\multicolumn{7}{|c|}{ MGT }{}\\\hline
		 Participant number & 1 & 7 & 8 & 9 & ~ & ~ & ~ \\\hline
		 Person-months per participant: & 9 & 3 & 3 & 3 & ~ & ~ & ~ \\\hline
	\end{tabular}
\end{table}

\subsubsection{Objectives}
\begin{itemize}
	\item O1.1 Meet Project Milestones: The management aims for keeping the project on track and meet the milestones. To achieve this, state of the art project management tools will be used such as \gls{RTC}. The Universities will be overseen by ELTE while the companies manage themselves. 
	
	\item O1.2 Manage Necessary Deliverables: The management aims for reporting annually a clear view over the project for supervisory authorities.  
\end{itemize}

\subsubsection{Description of work}
\begin{itemize}
	\item O1.1 Meet the Project Milestones
	\begin{itemize}
		\item T1.1.1: Bi-weekly management meetings should be held between the project participants and the meeting minutes should be stored at a central location accessible by all stakeholders.
		\item T1.1.2: Up-to-date reports should be available and presented at the stakeholder meetings. 
	\end{itemize}
	\item O1.2 Manage Necessary Deliverables:
	\begin{itemize}
		\item T1.2.1: The management should create and present the First Annual Report to the supervisory authorities.   
		\item T1.2.2: The management should create and present the Second Annual Report to the supervisory authorities.
		\item T1.2.3: The management should create and present the Final Annual Report to the supervisory authorities.
	\end{itemize} 
\end{itemize}

\subsubsection{Deliverables}

\begin{itemize}
	\item D1.1 First Annual Report: It should contain the work done during the first year and the achievements while introducing the time plan of next year. The report should be easily understandable for the authorities and should cover all fields of work.
	\item D1.2 Second Annual Report: It should contain the work done during the second year and the achievements while introducing the time plan of next year. The report should be easily understandable for the authorities and should cover all fields of work.  
	\item D1.3 Final Project Report:  It should contain the work done during the whole project life cycle and the achievements. The report should be easily understandable for the authorities and should cover all fields of work.  
\end{itemize}