\subsection{Work Package 8}

\begin{table}[hbpt]\centering
	\begin{tabular}{|p{0.35\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|
         p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|}\hline
		 Work package number& WP8 &
		 \multicolumn{4}{|c|}{Start date or starting event:}{}&
		 \multicolumn{2}{|c|}{                        1 }{}\\\hline
		 Work package title&\multicolumn{7}{|c|}{ Lessons Learned }{}\\\hline
		 Activity Type&\multicolumn{7}{|c|}{    OTHER}{}\\\hline
		 Participant number & 1 & 2 & 3 & 4 & 5 & 6 & ~ \\\hline
		 Person-months per participant: & 2 & 0.4 & 0.4 & 0.4 & 0.4 & 0.4 & ~ \\\hline
	\end{tabular}
\end{table}

\subsubsection{Objectives}
\begin{itemize}
	\item O8.1 Create Lessons Learned reports: WP responsibles  should be sure that needed data and information for reports are collected. Lessons Learned should be part of Annual Reports and Demonstrations. Lessons Learned reports should be sent to Annual Reports and Demonstration WP responsibles. 
	
	\item O8.2 Document mistakes and failures: Contributors should be reporting about their mistakes and failures. Data should be kept up-to-date and be in usable state.
\end{itemize}

\subsubsection{Description of work}
\begin{itemize}
	\item O8.1 Create Lessons Learned reports
	\begin{itemize}
		\item T8.1.1: Responsibles should create and present the \gls{NLP} Lessons Learned Report to the supervisory authorities.   
		\item T8.1.2: Responsibles should create and present the Semantic Analyzer Lessons Learned Report to the supervisory authorities.
		\item T8.1.3: Responsibles should create and present the Verifier Lessons Learned Report to the supervisory authorities.
		\item T8.1.4: Responsibles should create and present the Final Lessons Learned Report to the supervisory authorities.
	\end{itemize}
	\item O8.2 Keep collected data up-to-date
	\begin{itemize}
		\item T8.2.1: Monthly data from contributors shall be collected
		\item T8.2.2: Summarize and sent Lessons Learned reports to Annual Reports and Demonstration WP responsibles.
		\item T8.2.3: Update and validate last collected before every milestone  
	\end{itemize}
\end{itemize}

\subsubsection{Deliverables}
\begin{itemize}
	\item D8.1 \gls{NLP} Lessons Learned Report: The Lessons Learned report done after \gls{NLP} is finished should contain the mistakes and things what could have been done differently. The report should be easily understandable and be included into annual reports and demonstrations.
	\item D8.2 Semantic Analyzer Lessons Learned Report: The Lessons Learned report done after Semantic Analyzer is finished should contain the mistakes and things what could have been done differently. The report should be easily understandable and be included into annual reports and demonstrations.
	\item D8.3 Verifier Lessons Learned Report: The Lessons Learned report done after Verifier is finished should contain the mistakes and things what could have been done differently. The report should be easily understandable and be included into annual reports and demonstrations.
	\item D8.4 Final Lessons Learned Report: The Lessons Learned report done after the whole project is finished should contain the mistakes and things what could have been done differently. The report should be easily understandable and be included into final report and demonstrations.
\end{itemize}