\subsection{Work Package 9}

\begin{table}[hbpt]\centering
	\begin{tabular}{|p{0.35\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|
         p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|p{0.06\linewidth}|}\hline
		 Work package number& WP9 &
		 \multicolumn{4}{|c|}{Start date or starting event:}{}&
		 \multicolumn{2}{|c|}{                        1 }{}\\\hline
		 Work package title&\multicolumn{7}{|c|}{ Demonstration }{}\\\hline
		 Activity Type&\multicolumn{7}{|c|}{      DEM }{}\\\hline
		 Participant number & 1 & 7 & ~ & ~ & ~ & ~ & ~ \\\hline
		 Person-months per participant: & 3 & 1 & ~ & ~ & ~ & ~ & ~ \\\hline
	\end{tabular}
\end{table}

\subsubsection{Objectives}
	\begin{itemize}
		\item O9.1 Hold Annual and Final Demonstrations: WP responsibles  should be sure that needed data and tools for holding Annual and Final Demonstrations are collected. Lessons Learned should be part of Demonstrations. Members of every beneficiary should be sent and represent their organizations. 
		
		\item O9.2 Keep collected data up-to-date: Contributors should be reporting every month and before every milestone. Data should be kept up-to-date and every major change must be reported to the supervisory authorities.
		
		\item O9.3 Participate in FM 2021: Project aims to participate in "Formal Methods 2021" conference held in Beijing. Deadlines must be met.
	\end{itemize}

\subsubsection{Description of work}
\begin{itemize}
	\item O9.1 Hold Annual and Final Demonstrations
	\begin{itemize}
		\item T9.1.1: Responsibles should create and present the First Annual Demonstration to the supervisory authorities.   
		\item T9.1.1: Responsibles should create and present the Second Annual Demonstration to the supervisory authorities.
		\item T9.1.1: Responsibles should create and present the Final Annual Demonstration to the supervisory authorities.
	\end{itemize}
	\item O9.2 Keep collected data up-to-date
	\begin{itemize}
		 \item T9.2.1: Monthly data from contributors shall be collected
		 \item T9.2.2: Summarize most important data from Lessons Learned report and merge it into Annual Demonstrations
		 \item T9.2.3: Update and validate last collected before every milestone  
	\end{itemize}
	\item O9.3 Participate in FM 2021
	\begin{itemize}
		 \item T9.3.1: Create Description of Work for FM 2021
		 \item T9.3.2: Participate in FM 2021
		 \item T9.3.3: Retrospect participation and make report
	\end{itemize}
\end{itemize}

\subsubsection{Deliverables}
	\begin{itemize}
		\item D9.1 First Annual Demonstration: The work done during the first year should contain the achievements. The demonstration should be easily understandable for the authorities and should cover all fields of work. Demonstration should show aims for the next period.
		\item D9.2 Participation in FM 2021 Conference: The work which was done before conference should contain the achievements. The demonstration should cover importance and goals of work and its influence on state-of-the-art.
		\item D9.3 Second Annual Demonstration: The work done during the second year should contain the achievements. The demonstration should be easily understandable for the authorities and should cover all fields of work. Demonstration should show aims for the next period.
		\item D9.4 Final Project Demonstration: The work done during the whole year should contain the achievements. The demonstration should be easily understandable for the authorities and should cover all fields of work. Demonstration should show aims for the next period.
	\end{itemize}